---
title: "615 HW4"
output:
  html_document: default
  pdf_document: default
date: "2024-09-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###a 
Read in the data for all the years from 1985 to 2023.

```{r}
library(data.table)
years <- 1985:2023
file_root <- "https://www.ndbc.noaa.gov/view_text_file.php?filename=44013h"
tail <- ".txt.gz&dir=data/historical/stdmet/"
all_data <- list()
for (year in years) {
  path <- paste0(file_root, year, tail)
  header <- scan(path, what = 'character', nlines = 1)
  skip_lines <- ifelse(year < 2007, 1, 2)  
  buoy_data <- fread(path, header = FALSE, skip = skip_lines, fill = TRUE)
 if (ncol(buoy_data) == length(header)) {
    colnames(buoy_data) <- header
  } else {
    warning(paste("Data for year", year, "has inconsistent number of columns. Skipping header assignment."))
  }
  all_data[[as.character(year)]] <- buoy_data
}
```

```{r}
lapply(names(all_data), function(year) {
  cat("\nYear:", year, "\n")
  print(all_data[[year]])
})
```

###b
Identify and deal with the null data in the dataset.
```{r}
variables_na<-list(WDIR=99,
                   WVHT=99,
                   DPD=99, 
                   APD=99, 
                   MWD=999,
                   DEWP=999, 
                   VIS=99,
                   TIDE=99)
replace_na<-function(df, variables_na){
  for (col in names(variables_na)) {
    if (col %in% colnames(df)) {
      df[[col]][df[[col]] == variables_na[[col]]] <- NA
    }
  }
  return(df)
}
all_data <- replace_na(all_data, variables_na)
print(all_data)
```
$When null data has a specific interpretation in a dataset, it can be adjusted according to the context, rather than being directly converted to NA.$


###c
Use the Buoy data to see the effects of climate change:

$\To reflect the climate change trends, we can choose these variables: ATMP (Air temperature),WTMP(Sea surface temperature ), then analysis the overall trends between 1985 and 2023.$

```{r}
library(tidyverse)
library(data.table)
combined_data <- rbindlist(all_data, fill = TRUE, idcol = "year")
annual_avg <- combined_data %>%
  group_by(year) %>%
  summarize(
    avg_WTMP = mean(as.numeric(WTMP), na.rm = TRUE),
    avg_ATMP = mean(as.numeric(ATMP), na.rm = TRUE)
  )

ggplot(annual_avg, aes(x = as.numeric(year))) +
  geom_line(aes(y = avg_WTMP, color = "Sea surface Temperature")) +
  geom_line(aes(y = avg_ATMP, color = "Air Temperature")) +
  geom_smooth(aes(y = avg_WTMP), method = "lm", se = FALSE, linetype = "dashed", color = "blue") +
  geom_smooth(aes(y = avg_ATMP), method = "lm", se = FALSE, linetype = "dashed", color = "red") +
  labs(title = "Annual Average Temperatures (1985-2023)",
       x = "Year", y = "Temperature (°C)",
       color = "Temperature Type") 
```
$\The figure shows that the general trend of water temperature is down, and the general trend of air temperature is up. Extreme values have occurred in both cases.$

```{r}
wtmp_lm <- lm(avg_WTMP ~ year, data = annual_avg)
summary(wtmp_lm)
atmp_lm <- lm(avg_ATMP ~ year, data = annual_avg)
summary(atmp_lm)

```

###d
```{r}
rainfall_data<-read.csv("C:\\Users\\PC\\Desktop\\615\\Rainfall.csv", header= TRUE)
calculate_annual_rainfall <- function(rainfall_data) {
  rainfall_data <- rainfall_data %>%
    mutate(DATE = as.POSIXct(DATE, format = "%Y%m%d %H:%M"),  
           Year = year(DATE))  
  annual_rainfall <- rainfall_data %>%
    group_by(Year) %>%
    summarise(total_rainfall = sum(HPCP, na.rm = TRUE))  
  
  return(annual_rainfall)
}
annual_rainfall <- calculate_annual_rainfall(rainfall_data)
print(annual_rainfall)
```

```{R}
summary(annual_rainfall)
summary(buoy_data)

ggplot(annual_rainfall, aes(x = Year, y = total_rainfall)) +
  geom_line() +
  labs(title = "Rainfall in Boston (1985-2013)", x = "Year", y = "Rainfall (g)")

buoy_data %>%
  summarise(WTMP_avg = mean(WTMP, na.rm = TRUE),
            ATMP_avg = mean(ATMP, na.rm = TRUE))
```



